Within and beyond: chert procurement patterns during the Upper Palaeolithic in Southwesternmost Iberia

### 2024-10-21 analysis/paper/paper.qmd
Corrected legend from the indeterminate frequency table. N to number

```{r}
#| label: tbl-indet-freq
#| tbl-cap: N and percentage of grouped and indeterminate (INDET) artefacts by level in the Terrace (levels 4 to 7) and Shelter (A to C) areas.

>>>>

```{r}
#| label: tbl-indet-freq
#| tbl-cap: Number and percentage of grouped and indeterminate (INDET) artefacts by level in the Terrace (levels 4 to 7) and Shelter (A to C) areas.
